Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-08 longoutput.tex
Remove another unnecessary reference

Here we describe the scheme between the classical client and an honest quantum server. We mostly follow the logic in \cite{mahadev_delegation}. We first follow \cite{kempe_kitaev_regev_2006} to reduce the problem to an instance of local Hamiltonian.

@@

Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$. Here we follow \cite{PhysRevLett.120.040501} and \cite{PhysRevA.93.022326}.

>>>>

Here we describe the scheme between the classical client and an honest quantum server. This is similar to the underlying construction for \cite{mahadev_delegation}. We first preprocess the circuit using tools such as \cite{quant-ph/0301040}. We then follow \cite{kitaev2002classical} to reduce the problem to an instance of local Hamiltonian. We then analyze it using tools from \cite{PhysRevA.93.022326}. Then, NYI cuz we're stuck.

@@

Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$. Here we follow \cite{PhysRevA.93.022326}.
